Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2023-04-13 src/tex/ms.tex
[showyourwork] overleaf sync

    \begin{figure*}
        \script{example-fermi-lat.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/example-fermi-lat.pdf}
            \caption{
                Chandra Example
            }
            \label{fig:example-fermi-lat}
        \end{centering}
    \end{figure*}

>>>>

    \begin{figure*}
        \script{example-fermi-lat.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/example-fermi-lat.pdf}
            \caption{
                The \jolideco method applied to the supernova remnant \textit{RX J0852.0-4622} or \textit{Vela Junior}. The left image shows the counts above \qty[mode = text]{10}{GeV}. The different event classes are stacked into a single image.
                The image in the center show the flux reconstructed by the \jolideco methods. The image on the right shows the normalised residuals.
            }
            \label{fig:example-fermi-lat}
        \end{centering}
    \end{figure*}
